Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2022-12-18 manuscript/supplementaryRW.Rmd
change csl in supplementary

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: draft.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}

>>>>

---
title: "Supplementary figures\nCapturing regeneration in models of forest dynamics"
author: 
- Olalla Díaz-Yáñez, 
- Yannek Käber, 
- Mats Mahnken, 
- Samuel Fischer, 
- Xavier Morin, 
- Manfred Lexer, 
- Christian Hochauer, 
- Katarina Merganicova, 
- Tobias Mette, 
- Werner Rammer, 
- Kristin H. Braziunas, 
- Paola Mairota, 
- Josef Bruna,
- Heike Lischke, 
- Daniel Scherrer, 
- Simon Scheiter, 
- Thomas Hickler, 
- Tim Anders,
- Jessica Hetzer, 
- Harald Bugmann
date: "`r Sys.Date()`"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: global-change-biology.csl
editor_options: 
  markdown: 
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
